EDLD 651 Final Project Presentation

### 2020-11-30 presentation.Rmd
some more edits

## Challenges faced along the way
- Working with Git
  - Figuring out best practices for collaboration
- Working with GGPlot
  - Getting figures to display the right data
- Not getting distracted by all the pretty fractals

## Victories and things to celebrate
- We made our presentation in R
- We made a lot of sweet plots
- We worked well as a team
- I came away from this project knowing more about R than I did before

## Challenges you are still facing
- Touching up some plots
- Getting more efficient using Git

@@

## Challenges faced along the way
- Technological issues 
  - Version control
  - Multi OS nomenclature
  - Error bars

@@

## Victories and things to celebrate
- Technological work arounds
  - More familiar with path settings
  - General code interpretation and debugging improvements

## Challenges you are still facing
- Fluid coding
- More error feed back comprehension

@@

## Challenges faced along the way
- data wrangling
  - cleaning name 
  - large data sets
  - many separate data files for participants and conditions
  - needed to use both long and wide formats

## Victories and things to celebrate
- making GIFs
- super neat plots
- research question was answered
- hypothesis was correct
- using R to make this presentation

## Challenges you are still facing
- make some plots prettier

>>>>

## Challenges along the way
- Working with Git
  - Figuring out best practices for collaboration
- Working with GGPlot
  - Getting figures to display the right data
- Not getting distracted by all the pretty fractals

## Victories and celebrations
- We made our presentation in R
- We made a lot of sweet plots
- We worked well as a team
- I came away from this project knowing more about R than I did before

## Remaining Challenges
- Touching up some plots
- Getting more efficient using Git

@@

## Challenges along the way
- Technological issues 
  - Version control
  - Multi OS nomenclature
  - Error bars

@@

## Victories and and celebrations
- Technological work arounds
  - More familiar with path settings
  - General code interpretation and debugging improvements

## Remaining Challenges
- Fluid coding
- More error feed back comprehension

@@

## Challenges along the way

:::{}
- data wrangling
  - many separate data files
  - needed long and wide
  - cleaning names
:::

:::{}
 <img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/cleaning.png" height="250" width="400">
:::

## Victories and celebrations
- making GIFs
- super neat plots
- research question was answered
- hypothesis was correct
- using R to make this presentation

## Remaining Challenges
- make some plots prettier
